Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-12 paper/paper.tex
pass on example tests

\sloppy
\vspace{1ex}\noindent\textbf{Issue \#4, Table~\ref{tab:bugs}.} The
code snippet below shows a test that reveals a bug in \chakra.

@@

\vspace{1ex}\noindent\textbf{Issue \#18, Table~\ref{tab:bugs}.} The
snippet {\footnotesize\ttfamily{eval(function b(a)\{break;\});}}
revealed a bug in \veight{} version 7.0.244. This code snippet was
obtained by fuzzing a Test262 test with \quickfuzz. In its original
version, a string (omitted for space), passed as argument to the
\CodeIn{eval} function, encoded the actual test. The fuzzer replaced
the string argument with a function whose body is a \CodeIn{break}
statement outside a valid block statement. Section B.3.3.3 from the
\es\ spec~\cite{spec-b333} documents how eval should handle code
containing function declarations.  According to the
spec~\cite{break-statement}, the virtual machine should throw an early
error--in this case, a SyntaxError--if the break statement is not
nested in a loop or switch statement. All engines, but \veight{},
behave as expected in this case.

@@

\Mar{--------------- estou aqui}

\vspace{1ex}\noindent\textbf{Issue \#19,
  Table~\ref{tab:test-transplantation-bugs}.} The code snippet below
shows the test input we used to reveal a bug in \jsc.

@@

\vspace{1ex}\noindent\textbf{Issue \#2, Table~\ref{tab:bugs}.} We
reported the code snippet below to the \chakra\ development team as a
bug, but they did \emph{not} accept.

@@

\vspace{1ex}\noindent\textbf{Issue \#35, Table~\ref{tab:bugs}.} We
reported the code snippet below to the \smonkey\ development team as a
bug, the bug was confirmed in a few hours.

\begin{figure}[h!]
  \vspace{-0.5ex}
  \centering
  \scriptsize
  \lstset{escapeinside={@}{@},
%    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c,
    numberstyle=\tiny,
    morekeywords={assertEq, var, yield, in, function,
    typeof, return, throw, new, Error, if},
  }
  \begin{lstlisting}
    "use strict"
    010
  \end{lstlisting}
  \normalsize
  %% \caption{Warning captured as \hi{} priority.}
  %% \label{fig:hi-priority}
  \vspace{-1ex}
\end{figure}

This is a test case original from the \hermes suite using test transplantation.
According the specification, in strict mode, the engine must use
the prefix '0o' or '0O' to represents octal numeric literals. It was an
issue which explores a deprecated octal token after ASI (Automatic Semicolon Insertion).
The others engine throws a SyntaxError due the missing of the octal token, but
\smonkey returns a integer 8 that represents 010 in octal literal.

>>>>

\sloppy
\vspace{1ex}\noindent\textbf{Issue \#4, Table~\ref{tab:bugs}.} The
code snippet below shows a test that reveals a bug in \textbf{\chakra}.

@@

\vspace{1ex}\noindent\textbf{Issue \#18, Table~\ref{tab:bugs}.} The
snippet {\footnotesize\ttfamily{eval(function b(a)\{break;\});}}
revealed a bug in \textbf{\veight{}} version 7.0.244. This code snippet was
obtained by fuzzing a Test262 test with \quickfuzz. In its original
version, a string (omitted for space), passed as argument to the
\CodeIn{eval} function, encoded the actual test. The fuzzer replaced
the string argument with a function whose body is a \CodeIn{break}
statement outside a valid block statement. Section B.3.3.3 from the
\es\ spec~\cite{spec-b333} documents how eval should handle code
containing function declarations.  According to the
spec~\cite{break-statement}, the virtual machine should throw an early
error--in this case, a SyntaxError--if the break statement is not
nested in a loop or switch statement. All engines, but \veight{},
behave as expected in this case.

@@

\vspace{1ex}\noindent\textbf{Issue \#19,
  Table~\ref{tab:test-transplantation-bugs}.} The code snippet below
shows the test input we used to reveal a bug in \textbf{\jsc} version 234555.

@@

\vspace{1ex}\noindent\textbf{Issue \#2, Table~\ref{tab:bugs}.} We
reported the code snippet below to the \textbf{\chakra} development team as a
bug, but they did \emph{not} accept.

@@

\vspace{1ex}\noindent\textbf{Issue \#35, Table~\ref{tab:bugs}.} We
reported the snippet \CodeIn{"use strict" 010} to the
\textbf{\smonkey} development team as a bug and the bug was confirmed
in a few hours.  This is a test case original from the \hermes suite
using test transplantation.  According the specification, in strict
mode, the engine must use the prefix '0o' or '0O' to represents octal
numeric literals. It was an issue which explores a deprecated octal
token after ASI (Automatic Semicolon Insertion).  The others engine
throws a SyntaxError due the missing of the octal token, but \smonkey
returns a integer 8 that represents 010 in octal.

%% \begin{figure}[h!]
%%   \vspace{-0.5ex}
%%   \centering
%%   \scriptsize
%%   \lstset{escapeinside={@}{@},
%% %    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
%%     basicstyle=\ttfamily\scriptsize, boxpos=c,
%%     numberstyle=\tiny,
%%     morekeywords={assertEq, var, yield, in, function,
%%     typeof, return, throw, new, Error, if},
%%   }
%%   \begin{lstlisting}
%%     "use strict"
%%     010
%%   \end{lstlisting}
%%   \normalsize
%%   %% \caption{Warning captured as \hi{} priority.}
%%   %% \label{fig:hi-priority}
%%   \vspace{-1ex}
%% \end{figure}
